Visually pleasing knot projections

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

They may be fixed in two ways: Enhance the detailed explanations of
the choices made in creating package [27]; and add a more extended
discussion of a few things that might be approached differently in a
future package ( -- which can also handle links).

In view of this, I recommend that Appendices A and B should be firmly
integrated into the main text.  The discussions therein relate rather
directly to what I see as the main contribution of a JMA paper on this
topic.

A few comments on some rebuttals:

RE: Why use Bezier curves? : A key point, which should be mentioned in
the justification for Bezier curves, is that they interpolate their
end-points. This gives users a convenient, more direct control of
where these curve segments will appear than what they would get from
G2-continuous B-splines, which are only approximating their control
points.\textcolor{blue}{\\Fixed: sentence added to manuscript\\ \\}

@@

Page 6, line 20: How many (x,y) pairs are there?
\textcolor{blue}{\\Object {\tt k76} has a total of 49 lines and I have
  indicated this in the text.  Old text: ``Above we see only the first
  six lines of the object".  New text: ``The object has 49 lines, of
  which only the first six are shown".\\ \\}

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\simeq 50$ for the knots
  presented here".\\ \\}

Page 6, Line 39: ``... the overall bending energy." {\tt ->>} 'minimizing
overall bending energy.'
\textcolor{blue}{\\Fixed\\ \\}

Page 6, Line 42: What is "{\tt > b <}" ?  \textcolor{blue}{\\ This is
  just a detail of standard R syntax.  The first ``{\tt > }" is just
  the R prompt; letter {\tt b} is just a variable; and the symbol
  ``{\tt <-}" usually has a gloss of ``becomes".  Thus {\tt b <- 4} is
  read ``{\tt b} becomes 4". The reason I need a variable is that I
  want to show the result of applying two functions, {\tt
    total\_crossing\_angles()} and {\tt total\_bending\_energy()}, to
  the same variable {\tt b}.\\ \\}

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

For each crossing point, the user would see an orthogonal "cross-hair"
that can be shifted and rotated as a whole.  In addition, there are
two parameters (handle-pairs) that control the "velocities" of the two
strands through the crossing.  The optimization routine would
fine-tune these velocities to achieve matching curvature for the two
sequentially connected Bezier curves.

And, yes, if a crossing point falls on a line of mirror symmetry, the
crosshair would automatically be angled at 45 degrees with respect to
this line.  And if the knot has n-fold rotational symmetry, n such
cross hairs would be placed at the vertices of a regular n-gon.  (All
this is not such a "nightmare" if it is properly considered from the
beginning.)

I don't expect that anything in the current system should be changed;
but this approach should definitely be considered in a future version
of such a package.

RE: Mismatched diagram and symmetry specifications: ``This situation
cannot occur" -- If the user makes a mistake, will the current system
send a suitable error message?\textcolor{blue}{\\For convenience, I
  reproduce the original exchange below:\\ \\} {\tiny Reviewer's
  comment, round 3: ``If all nodes fulfill the specified symmetry
  constraints (as shown on page 11, lines 15-22 and on lines 35-43),
  but the connection diagram does not completely adhere to the
  specified symmetry - What happens? - Does the package check this and
  let the user know about the discrepancy?"}  \textcolor{blue}{\tiny
  My original reply: ``This situation cannot occur: symmetric nodes
  imply a symmetric diagram".\\ \\} \textcolor{blue}{A more nuanced
  reply would be to observe that in the event of a mismatch between
  diagram and symmetry specifications, the symmetry specifications
  take priority and the resulting symmetrised diagram automatically
  accommodates the imposed symmetry.  In practice what happens is
  immediately visually apparent: one sees beautiful symmetric nodes
  joined by Bezier curves that do not posess the intended topology.
  The diagram is a disorganised ugly tangled mess, clearly not
  reflecting the intended configuration.  In practice, one glance at
  the diagram simultaneously reveals the problem and its solution
  (just reconnect the dots in the correct order).\\ \\}

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

I don't expect that anything in the current system should be changed;
but this approach should definitely be considered in a future version
of such a package.

RE: Mismatched diagram and symmetry specifications: ``This situation
cannot occur" -- If the user makes a mistake, will the current system
send a suitable error message?\textcolor{blue}{\\For convenience, I
  reproduce the original exchange below:\\ \\} {\tiny Reviewer's
  comment, round 3: ``If all nodes fulfill the specified symmetry
  constraints (as shown on page 11, lines 15-22 and on lines 35-43),
  but the connection diagram does not completely adhere to the
  specified symmetry - What happens? - Does the package check this and
  let the user know about the discrepancy?"}  \textcolor{blue}{\tiny
  My original reply: ``This situation cannot occur: symmetric nodes
  imply a symmetric diagram".\\ \\} \textcolor{blue}{A more nuanced
  reply would be to observe that in the event of a mismatch between
  diagram and symmetry specifications, the symmetry specifications
  take priority and the resulting symmetrised diagram automatically
  accommodates the imposed symmetry.  In practice what happens is
  immediately visually apparent: one sees beautiful symmetric nodes
  joined by Bezier curves that do not posess the intended topology.
  The diagram is a disorganised ugly tangled mess, clearly not
  reflecting the intended configuration.  In practice, one glance at
  the diagram simultaneously reveals the problem and its solution
  (just reconnect the dots in the correct order).\\ \\}

RE: A hierarchical way of dealing with symmetry: "This is exactly what
I have done!  The referee gives an accurate summary of the code's
methodology."  - Place a corresponding, extended description into the
main text.

RE: A slider interface for changing some optimization parameters: It
is clear why this would not be practical in the current system, where
the optimization of a pretzel knot ``may take a few weeks."  But this
also suggests that there is much room for improvement!  Perhaps some
badness functions are not really needed or are badly implemented.
\textcolor{blue}{\\ This is an excellent suggestion and indeed many of
  the badness functions may well turn out to be superfluous, or at
  least susceptible to faster heuristics [although I would argue that
    the functions all adhere to efficient vectorised R coding
    standards].  If it turns out that some of the badness weightings
  can be set to zero without degrading the resulting visual
  attractiveness, this would certainly be worth pursuing.\\ \\}

### 2023-02-01 inst/jma_rebuttal_2023_01_30.tex

Many of the important badness functions (e.g. separations of nodes or
of non-crossing curve segments) are based purely on local geometry and
need not know what component of a link they refer to.  Perhaps the
overall length of a knot or of a link-component is not a good metric,
and should be replaced with some other functions of the length of
curve segments between crossings.

Some detailed comments on manuscript R2:

Page 6, line 20: How many (x,y) pairs are there?
\textcolor{blue}{\\Object {\tt k76} has a total of 49 lines and I have
  indicated this in the text.  Old text: ``Above we see only the first
  six lines of the object".  New text: ``The object has 49 lines, of
  which only the first six are shown".\\ \\}

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\gtrsim 50$ for the knots
  presented here".\\ \\}

@@

Page 6, Line 42: What is "{\tt > b <}" ?  \textcolor{blue}{\\ This is
  just a detail of standard R syntax.  The first ``{\tt > }" is just
  the R prompt; letter {\tt b} is just a variable; and the symbol
  ``{\tt <-}" usually has a gloss of ``becomes".  Thus {\tt b <- 4} is
  read ``{\tt b} becomes 4". The reason I need a variable is that I
  want to show the result of applying two functions, {\tt
    total\_crossing\_angles()} and {\tt total\_bending\_energy()}, to
  the same variable {\tt b}.\\ \\}

Figures 3 and 5: Try running these figures with only 50 points (and
circles) for each Bezier segment.

Figure 4 caption: Much of the explanation of "7 3" versus "3 7" is
already in the main text.  \textcolor{blue}{\\Fixed\\ \\}

Page 8, Line 60: "Why 64 real variables"?  What are they?  How does
this agree with "R50" on page 6?\textcolor{blue}{\\ The 64 variables are just the parameters required to describe the knot path, it agrees with the (reworded) coment about $\mathbb{R}^{50}$.\\ \\}

### 2023-02-01 inst/jma_knot.tex
fixes #82
fixes #100
fixes #94 also refers issue #89

\documentclass{birkjour}
%%%Optional but convenient to use is the package ``cite''. If you do not want to use, remark the next line by placing the percent sign % in front of it:
\usepackage[noadjust]{cite}
\usepackage{amsmath}
%
%
% THEOREM Environments (Examples)-----------------------------------------
%
 \newtheorem{thm}{Theorem}[section]
 \newtheorem{cor}[thm]{Corollary}
 \newtheorem{lem}[thm]{Lemma}
 \newtheorem{prop}[thm]{Proposition}
 \theoremstyle{definition}
 \newtheorem{defn}[thm]{Definition}
 \theoremstyle{remark}
 \newtheorem{rem}[thm]{Remark}
\newtheorem{comment}[thm]{Comment}
 \newtheorem*{ex}{Example}
 \numberwithin{equation}{section}

@@

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{Inkscape}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection; here cubic Bezier curves are
used.  Bezier curves are a natural choice for working with
mathematical knots for several reasons: they are familiar to many
graphical workers; they have a natural and intuitive control system
(usually called ``handles''), and are implemented in many graphical
software suites.  The software discussed here~\cite{hankin2020} allows
one to specify a knot in terms of its Bezier control points within
inkscape, import the object into R~\cite{rcore2021}, and then to use
numerical optimization techniques to improve the visual appearance of
the knot.

@@

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.  In the package, minimization is
performed using either Nelder-Mead~\cite{nelder1965} or a Newton-type
method~\cite{dennis1983} (gradient information is not available).  The
optimization proceeds over $\mathbb{R}^n$ where $n$ is the number of
parameters needed to specify the path; typically $n\simeq 50$ for the
knots presented here.  In the context of the package, the methods
appear to be broadly comparable.

>>>>

\documentclass{birkjour}
%%%Optional but convenient to use is the package ``cite''. If you do not want to use, remark the next line by placing the percent sign % in front of it:
\usepackage[noadjust]{cite}
\usepackage{amsmath}
\usepackage{url}
%
%
% THEOREM Environments (Examples)-----------------------------------------
%
 \newtheorem{thm}{Theorem}[section]
 \newtheorem{cor}[thm]{Corollary}
 \newtheorem{lem}[thm]{Lemma}
 \newtheorem{prop}[thm]{Proposition}
 \theoremstyle{definition}
 \newtheorem{defn}[thm]{Definition}
 \theoremstyle{remark}
 \newtheorem{rem}[thm]{Remark}
\newtheorem{comment}[thm]{Comment}
 \newtheorem*{ex}{Example}
 \numberwithin{equation}{section}

@@

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{Inkscape}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection; here cubic Bezier curves are
used.  This gives users a convenient, direct control of where these
curve segments will appear; compare G2-continuous B-splines, which
only approximate their control points.

Bezier curves are a natural choice for working with
mathematical knots for several reasons: they are familiar to many
graphical workers; they have a natural and intuitive control system
(usually called ``handles''), and are implemented in many graphical
software suites.  The software discussed here~\cite{hankin2020} allows
one to specify a knot in terms of its Bezier control points within
inkscape, import the object into R~\cite{rcore2021}, and then to use
numerical optimization techniques to improve the visual appearance of
the knot.

@@

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.  In the package, minimization is
performed using either Nelder-Mead~\cite{nelder1965} or a Newton-type
method~\cite{dennis1983} (gradient information is not available).  The
optimization proceeds over $\mathbb{R}^n$ where $n$ is the number of
parameters needed to specify the path; typically $n\gtrsim 50$ for the
knots presented here.  In the context of the package, the methods
appear to be broadly comparable.
